Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-24 paper/paper.tex
Added method of moments and alpha techniques to similarity.py and experiment.py. Added momentsTrain.py and alphaParams.py to get parameters for these techniques. Added technique descriptions to paper

The model suggests that there is a linear correlation between $X_n$, the
similarity calculated with $n$ common users, and $Y$, the true similarity. Since 
$\sigma_{2,n}^2\ge0$, the slope is always $\le1$, meaning that the calculated
distance from $\mu$ (the average similarity) overestimates the true distance. This makes
sense, since there is a prior distribution of true similarity weighted around $\mu$.

@@

\section*{Technique}

\begin{itemize}
    \item Discussion of abandonment of parameterization in exchange for linear regression
    \item Pick data that's big enough to have gold standard
    \item Slice data and group by n
    \item Run linear regression on each group of n
    \item For predicting true similarity, take a given point and project on appropriate
    \item regression.
\end{itemize}

>>>>

The model suggests that there is a linear correlation between $X_n$, the
similarity calculated with $n$ common users, and $Y$, the true similarity.
Moreover, the best predicted $y$ is a linear combination of the mean and the
observed similiatiry. Since $\sigma_{2,n}^2\ge0$, the slope is always $\le1$, 
meaning that the calculated distance from $\mu$ (the average similarity) 
overestimates the true distance. This makes sense, since there is a prior 
distribution of true similarity weighted around $\mu$.

@@

\section*{Technique}
Based on this maodel, we try three different techniques to predict the true similarity from a
measured similarity. The techniques vary in their fidelity to the model. For
each, we limit our data to all pairs of items that have enough common users that
we can approximate $TrueSim \approx Sim$. Then we pick subsets of the common
users of various sizes $n$ and calculate $Sim_{n}$. With examples of $Sim$, $n$
and the resulting $TrueSim$, we can implement supervised learning.

The first technique is the least faithful to the model. It simply runs a number
of linear regressions between $Sim$ and $TrueSim$ for each $n$. This ignores the 
data-specific parameters $\mu$, $\sigma_{1}$ and $\sigma_{2,n}$ to find the best 
linear fit. It also treats each $n$ completely independently. This technique 
necessarilty has the lowest training error of all linear techniques, potentially 
at the risk of overfitting.

The second technique is more general. It approximates $\mu$ and $\sigma_{1}$
using the method of moments on the training data of all $TrueSim$ scores. Then,
$\sigma_{2,n}$ is also approximated using a method of moments on the training
data of all $Sim_n$ for each $n$ separately. Here $\sigma_{2,n}$'s are also
considered independently of each other.

The third and most general technique models $\sigma_{2,n}$ as a function of
$n$ using equation 19. As in the previous technique, $\mu$, $\sigma_{1}$ and each
$\sigma_{2,n}$ are approximated using the method of moments over the training
data. Then $\alpha$ is calculated that minimizes the sum of squared errors
between $\sigma_{2,n}^2$ and $\frac{\alpha}{\sqrt{n}}$. This $\alpha$ is used to
construct the three-parameter prediction function of equation 19.
